Topological Equivariant Artist Model for Visualization Library Architecture

### 2022-04-21 paper/main.tex
math implementation bridge

The \textcolor{base}{base space} is a topological space \dbasec\ with points $\dbasepointc \in \dbasec$ and topology $\mathcal{T}_{\dbasec}$; $\mathcal_{T}_k$ is a set of opensets $ \dbasepointc \in \opensetc \subseteqq \dbasec$ \cite{munkresElementsAlgebraicTopology1984} that cover the base space \dbasec.  The \textcolor{fiber space} is a topological space \dfiberc\ that is the preimage of the projection function $\pi$ at a point in the base space $\dfiberc|_{\dbasepointc} = \pi^{-1}(\dbasepointc)$ and fibers of a bundle are isomorphic $\dfiberc \simeq \dfiberc_{\dbasepointc}\;\forall \dbasepointc \in \dbase$. The \textcolor{section}{sections} of a bundle $\dsection$ are maps from the base space to points in the bundles over that base space and $\textcolor{set}{\Gamma}$ denotes the set of all sections in a bundle over an openset. 
\begin{equation}
  \label{eq:atct:fb_sections}
  \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} \coloneqq \big\{\dsectionc: \opensetc\rightarrow \dtotalc\restriction_{\opensetc} \; \bigm{\vert} \pi(\dsectionc(\dbasepointc)) = \dbasepointc\;for\, all\; \dbasepointc \in \opensetc \big\} 
\end{equation}

@@

Fiber bundles can be used to model data for visualization, as proposed by Butler\cite{butlerVectorBundleClassesForm1992, butlerVisualizationModelBased1989}. We describe the topological properties of the data \cite{wilkinsonGrammarGraphics2005} as the base space \dbasec. The topological properties, as described by Wilkenson, are how the data is organized - for example \dbase\ could be discrete points, a line, a 2D surface, a 3D volume, or a graph. The names and data types of the data fields can be expressed as the fiber space \dfiberc, as described by Spivak \cite{spivakDatabasesAreCategories2010,spivakSIMPLICIALDATABASES}. For example, a temperature field could be expressed as a fiber $\dfiber_{temperature}=\mathbb{R}$, and a color field could be $\dfiber_{color}=\mathbb{R}^{3}$. Even though fibers on non-trivial spaces, such as vector fields, are different, we can simplify to one type because fibers are isomorphic.\note{unsure of this claim but I think this is why, and also I need to tell you why you care that they're isomorphic} The total bundle space \dtotalc\ acts as a way of expressing all data with the same topolology \dbasec\ and fields \dfiberc, for example a database schema. A specific dataset is represented as a section \dsectionc, and the return values of a section evaluated at a point \dbasepointc\ is the record $\{field_{0}: value_{0}, ..., field_n:value_n\}$ at that point.

@@

\subsection*{Testing Equivariance}
\begin{equation*}
  \begin{tikzcd}[row sep=huge]
    \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}}
    \arrow[d, "\equivc", color=monoid]
     \arrow[rr, "\vartistc", color=artist] &  & \imartist{\opensetgc}{\gtotalc\restriction_{\opensetgc}} 
     \arrow[d, "\extractmc", color=monoid] \arrow[r, "render"] & VIZ \arrow[ld, "measure"] \\
    {Hom(\opensetc, \measurec)} \arrow[rr, "\vindexpullc", color=functor]  &  & {Hom(\opensetgc, \measurec)}   & 
    \end{tikzcd}
  \end{equation*}
  \begin{description}
      \item[expected]{$\equivc: \dsectionc \mapsto (\opensetc \xrightarrow{\equivc_{\dsectionc}} \measurec)$}
      \item[actual]{$\extractmc:\gsectionc \mapsto (\opensetgc \xrightarrow{\extractmc_{\gsectionc}} \measurec)$}
      \item[] $\equivc_{\dsectionc}(\dbasepointc) = \extractmc_{\gsectionc}(\gbasepointc)$ for all $\vindexc(\gbasepointc) = \dbasepointc, \dbasepointc \in \dbasec, \gbasepointc \in \gbasec$ 
  \end{description}

@@

\subsection{$\vindexc: \gbasec \rightarrow \dbasec$}
We define the functor $\vindex$ such that the data base space \dbase\ is a deformation retraction\cite{nlab:deformation_retract} of the graphic space $\gbase$, meaning that there is a continuous surjective mapping from every point $\dbasepoint\in\dbase$ to a point $\dbasepoint \in dbase$ . To simplify matters, in this paper, we construct the graphic space as a constant multiple of the base space such that 
\begin{equation}
  \underbrace{\opensetc\times[0,1]^{n}}_{\opensetgc} \textcolor{functor}{\xmapsto{\hspace{1em}\vindexc\hspace{1em}}} \opensetc} 
\end{equation}
\begin{equation*}
  n = \begin{cases}
    dim(\gbase) - dim(\dbase) & dim(\dbase)<dim(\gbase)\\
  0 & otherwise
  \end{cases}
\end{equation*}

\subsection{$\nu: \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} \rightarrow \cgamma{\opensetc}{\vtotalc\restriction_{\opensetc}}$}
The transformation $\vchannel$ is a pointwise transformation $\pi(\dtotal) = \pi(\vchannel(\dtotal))$ such that 
\begin{equation}
  \label{eq:constrution:nu}
  \vchannelc: \dfiberc_{\dfiberc} \rightarrow \vfiberc_{\dbasepoint}
\end{equation}
which means that every point in a data fiber $\delement \in \dfiber_{\dbasepointc}$ can be mapped into a correspoindg point in the visual fiber $\velement \in \vfiber_{\dbasepointc}$. A pair of transformations $(\vchannel, \vchannel^{\prime})$ are equivariant if 
\begin{equation}
  \dfunct_{\vtotal} \vchannel(\dsection(\dbasepoint)) = \vchannel^{\prime}(\dfunct_{\dtotal}(\dsection(\dbasepoint)))\; \forall \dbasepoint \in \dbase
\end{equation}
and a transformation $\vchannel$ is equivariant when $\vchannel = \vchannel^{\prime}$
\subsection*{Compositing \vchannelc's}

\begin{equation}
  \begin{tikzcd}[col sep=Huge]
    \dfiberc_{\dbasepointc} 
    \arrow[rr, "\vchannelc", color=artist] 
    \arrow[rrrr, "\vchannelc^{\prime\prime}", dashed, bend right, color=artist] &  & 
    \vfiberc_{\dbasepointc}\coloneqq{\dfiberc_{\dbasepointc}^{\prime}} 
    \arrow[rr, "\vchannelc^{\prime}", color=artist] &  & 
    \vfiberc^{\prime}_{\dbasepointc}
  \end{tikzcd}
\end{equation}

\subsection*{Sharing \vchannelc's}
\begin{equation}
  \begin{tikzcd}[column sep=4em]
    {\dfiberc_{\dbasepointc}^{a}} \times {\dfiberc_{\dbasepointc}^{b}} 
    \arrow[d, "\pi_a"', color=fiber] 
    \arrow[r, "\vchannelc_{ab}", color=artist] 
    \arrow[rr, "\equivc_{ab}", bend left, color=monoid]  & 
    {\vfiberc_{\dbasepointc}^{a}} \times {\vfiberc_{\dbasepointc}^{b}} 
    \arrow[d, "\pi_a", color=fiber] & 
    \measurec_{\dbasepointc}^{ab} 
    \arrow[d, "\measurec^{ab}\restriction_a", color=set] \\
    \dfiberc_{\dbasepointc}^a 
    \arrow[r, "\vchannelc_{a}", dashed, color=artist] & 
    \vfiberc_{\dbasepointc}^a 
    \arrow[r, "\simeq", dotted]  & 
    \measurec_{\dbasepointc}^a   \\
    {\dfiberc_{\dbasepointc}^{a}} \times {\dfiberc_{\dbasepointc}^{c}} 
    \arrow[u, "\pi_a", color=fiber] 
    \arrow[r, "\vchannelc_{ac}", color=artist] 
    \arrow[rr, "\equivc_{ac}", bend right, color=monoid] & 
    {\vfiberc_{\dbasepointc}^{a}} \times {\vfiberc_{\dbasepointc}^{c}} 
    \arrow[u, "\pi_a"', color=fiber] & 
    \measurec_{\dbasepointc}^{ac} 
    \arrow[u, "\measurec^{ac}\restriction_a"', color=set]            
    \end{tikzcd}
\end{equation}

\subsection{$\vmarkc: \cgamma{\opensetc}{\vtotalc\restriction_{\opensetc}} \rightarrow \cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}}$}
\subsubsection{Fabricating \vmarkc's}

@@

\subsubsection{Combining \vmarkc's}

\subsubsection{Shared Visual Encodings}
\begin{equation}
  \begin{tikzcd}[row sep=2.5em, column sep=.75sem]
    &  & \imartistsub{ab}{\opensetgc}{\gtotalc\restriction\opensetgc}
    \arrow[rrd, "\extractmc_{bc}", color=monoid] &  &  \\
\cgamma{\opensetc}{\vtotalc^{a}\restriction_{\opensetc}\times \vtotalc^{b}\restriction_{\opensetc}} 
\arrow[rru, "\vmarkc_{ab}", color=artist] 
\arrow[d, "\pi_a"', color=total] &  &  &  & 
{{\textcolor{set}{Hom}(\opensetgc, \measurec^{ab})}} 
\arrow[d, "\measurec^{ab}\restriction_a", color=set]  \\
\cgamma{\opensetc}{\vtotalc^{a}\restriction_{\opensetc}} 
\arrow[rr, "\simeq", dotted]  &  & 
{{\textcolor{set}{Hom}(\opensetc, \measurec^{a})}} 
\arrow[rr, "\vindexpullc", color=functor] &  & 
{{\textcolor{set}{Hom}(\opensetgc, \measurec^{a})}} \\
\cgamma{\opensetc}{\vtotalc^{a}\restriction_{\opensetc}\times \vtotalc^{c}\restriction_{\opensetc}} 
\arrow[rrd, "\vmarkc_{bc}", color=artist] 
\arrow[u, "\pi_a", color=total]  &  &  &  & 
{{\textcolor{set}{Hom}(\opensetgc, \measurec^{ac})}} 
\arrow[u, "\measurec^{ab}\restriction_a"', color=set] \\
 &  & \imartistsub{ac}{\opensetgc}{\gtotalc\restriction\opensetgc}
 \arrow[rru, "\extractmc_{ab}", color=monoid] &  & 
\end{tikzcd}
\end{equation}
\note{when Q_{ab} = Q_{bc}, this says only things that change are the parameter controlled pieces}

>>>>

The \textcolor{base}{base space} is a topological space \dbasec\ with points $\dbasepointc \in \dbasec$ and topology $\mathcal{T}_{\dbasec}$; $\mathcal{T}_k$ is a set of opensets $ \dbasepointc \in \opensetc \subseteqq \dbasec$ \cite{munkresElementsAlgebraicTopology1984} that cover the base space \dbasec.  The \textcolor{fiber}{fiber space} is a topological space \dfiberc\ that is the preimage of the projection function $\pi$ at a point in the base space $\dfiber_{\dbasepointc} = \pi^{-1}(\dbasepointc)$ and fibers of a bundle are isomorphic $\dfiberc \simeq \dfiberc_{\dbasepointc}\;\forall \dbasepointc \in \dbase$. The \textcolor{section}{sections} of a bundle $\dsection$ are maps from the base space to points in the bundles over that base space and $\textcolor{set}{\Gamma}$ denotes the set of all sections in a bundle over an openset. 
\begin{equation}
  \label{eq:atct:fb_sections}
  \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} \coloneqq \big\{\dsectionc: \opensetc\rightarrow \dtotalc\restriction_{\opensetc} \; \bigm{\vert} \pi(\dsectionc(\dbasepointc)) = \dbasepointc\;for\, all\; \dbasepointc \in \opensetc \big\} 
\end{equation}

@@

Fiber bundles can be used to model data for visualization, as proposed by Butler\cite{butlerVectorBundleClassesForm1992, butlerVisualizationModelBased1989}. We describe the topological properties of the data \cite{wilkinsonGrammarGraphics2005} as the base space \dbasec. The topological properties, as described by Wilkenson, are how the data is organized - for example \dbase\ could be discrete points, a line, a 2D surface, a 3D volume, or a graph. The names and data types of the data fields can be expressed as the fiber space \dfiberc, as described by Spivak \cite{spivakDatabasesAreCategories2010,spivakSIMPLICIALDATABASES}. For example, a temperature field could be expressed as a fiber $\dfiber_{temperature}=\mathbb{R}$, and a color field could be $\dfiber_{color}=\mathbb{R}^{3}$. Even though fibers on non-trivial spaces, such as vector fields, are different, we can simplify to one type because fibers are isomorphic.\note{unsure of this claim but I think this is why, and also I need to tell you why you care that they're isomorphic} The total bundle space \dtotalc\ acts as a way of expressing all data with the same topology \dbasec\ and fields \dfiberc, for example a database schema. A specific dataset is represented as a section \dsectionc, and the return values of a section evaluated at a point \dbasepointc\ is the record $\{field_{0}: value_{0}, ..., field_n:value_n\}$ at that point.

@@

\subsection*{Testing Equivariance}
\begin{equation}
  \begin{tikzcd}[row sep=huge]
    \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} 
    \arrow[rr, "\vartistc", color=artist] 
    \arrow[d, "\equivc"', color=monoid] &  & 
    \cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}} 
    \arrow[d, "render"] 
    \arrow[lld, "\extractmc"', color=monoid, dashed] \\
    {\textcolor{set}{Hom}(\opensetc, \measurec)}  &  & visualization 
    \arrow[ll, "measure",]
    \end{tikzcd}
  \end{equation}
  \begin{description}
      \item[expected]{\;$\equivc: \dsectionc \mapsto (\opensetc \xrightarrow{\equivc_{\dsectionc}} \measurec)$}
      \item[actual]{$\extractmc:\gsectionc \mapsto (\opensetc \xrightarrow{\extractmc_{\gsectionc}} \measurec)$}
    \end{description}
    such that
    \begin{equation}
    \equivc(\dsectionc)(\dbasepointc) = \extractmc(\vartistc(\dsectionc))(\dbasepointc) = \extractmc(\gsectionc\circ\vindexprec)(\dbasepointc)
    \end{equation}

@@

\subsection{$\vindexc: \gbasec \rightarrow \dbasec$}
We define the functor $\vindex$ such that the data base space \dbase\ is a deformation retraction\cite{nlab:deformation_retract} of the graphic space $\gbase$, meaning that there is a continuous surjective mapping from every point $\dbasepoint\in\dbase$ to a point $\dbasepoint \in dbase$ . To simplify matters, in this paper, we construct the graphic space as a constant multiple of the base space such that 
\begin{equation}
  \underbrace{\opensetc\times[0,1]^{n}}_{\opensetgc} \textcolor{functor}{\xmapsto{\hspace{1em}\vindexc\hspace{1em}}} \opensetc 
\end{equation}
\begin{equation*}
  n = \begin{cases}
    dim(\gbase) - dim(\dbase) & dim(\dbase)<dim(\gbase)\\
  0 & otherwise
  \end{cases}
\end{equation*}

\subsection{$\nu: \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} \rightarrow \cgamma{\opensetc}{\vtotalc\restriction_{\opensetc}}$}
The transformation $\vchannel$ is a pointwise transformation $\pi(\dtotal) = \pi(\vchannel(\dtotal))$ such that 
\begin{equation}
  \label{eq:constrution:nu}
  \vchannelc: \dfiberc_{\dfiberc} \rightarrow \vfiberc_{\dbasepoint}
\end{equation}
which means that every point in a data fiber $\delement \in \dfiber_{\dbasepointc}$ can be mapped into a correspoindg point in the visual fiber $\velement \in \vfiber_{\dbasepointc}$. A pair of transformations $(\vchannel, \vchannel^{\prime})$ are equivariant if 
\begin{equation}
  \dfunct_{\vtotal} \vchannel(\dsection(\dbasepoint)) = \vchannel^{\prime}(\dfunct_{\dtotal}(\dsection(\dbasepoint)))\; \forall \dbasepoint \in \dbase
\end{equation}
and a transformation $\vchannel$ is equivariant when $\vchannel = \vchannel^{\prime}$
\subsection*{Fabricating \vchannelc's}

\begin{equation}
  \begin{tikzcd}[col sep=Huge]
    \dfiberc_{\dbasepointc} 
    \arrow[rr, "\vchannelc", color=artist] 
    \arrow[rrrr, "\vchannelc^{\prime\prime}", dashed, bend right, color=artist] &  & 
    \vfiberc_{\dbasepointc}\coloneqq{\dfiberc_{\dbasepointc}^{\prime}} 
    \arrow[rr, "\vchannelc^{\prime}", color=artist] &  & 
    \vfiberc^{\prime}_{\dbasepointc}
  \end{tikzcd}
\end{equation}
\subsubsection{Combining \vchannelc's} 
We can add visual parameters as

\subsection*{Validating \vchannelc's}
\begin{equation}
  \begin{tikzcd}[column sep=4em]
    {\dfiberc_{\dbasepointc}^{a}} \times {\dfiberc_{\dbasepointc}^{b}} 
    \arrow[d, "\pi_a"', color=fiber] 
    \arrow[r, "\vchannelc_{ab}", color=artist] 
    \arrow[rr, "\equivc_{ab}", bend left, color=monoid]  & 
    {\vfiberc_{\dbasepointc}^{a}} \times {\vfiberc_{\dbasepointc}^{b}} 
    \arrow[d, "\pi_a", color=fiber] & 
    \measurec_{\dbasepointc}^{ab} 
    \arrow[d, "\measurec^{ab}\restriction_a", color=set] \\
    \dfiberc_{\dbasepointc}^a 
    \arrow[r, "\vchannelc_{a}", dashed, color=artist] & 
    \vfiberc_{\dbasepointc}^a 
    \arrow[r, "\simeq", dotted]  & 
    \measurec_{\dbasepointc}^a   \\
    {\dfiberc_{\dbasepointc}^{a}} \times {\dfiberc_{\dbasepointc}^{c}} 
    \arrow[u, "\pi_a", color=fiber] 
    \arrow[r, "\vchannelc_{ac}", color=artist] 
    \arrow[rr, "\equivc_{ac}", bend right, color=monoid] & 
    {\vfiberc_{\dbasepointc}^{a}} \times {\vfiberc_{\dbasepointc}^{c}} 
    \arrow[u, "\pi_a"', color=fiber] & 
    \measurec_{\dbasepointc}^{ac} 
    \arrow[u, "\measurec^{ac}\restriction_a"', color=set]            
    \end{tikzcd}
\end{equation}

\subsection{Graphic Compositing Function}
The compositing function $\vmarkc$ transforms the sections of visual elements $\vsectionc$ into sections of graphics $\gsectionc$.
\begin{equation}
  \vmarkc: \cgamma{\opensetc}{\vtotalc\restriction_{\opensetc}} \rightarrow \cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}}
\end{equation}

\note{some transition about sheaf morphisms}
Therefore an equivariant $\vmarkc$ satisfies the conditions....

\subsubsection{Fabricating \vmarkc's}

@@

\subsubsection{Combining \vmarkc's}
A set of $\vmarkc$ functions that output graphic sections, as introduced in \autoref{eq:atct:fb_graphic_section}, that go to the same space, for example to the same figure in a screen, are returning a set of functions into the same total bundle $\gtotal$;
\begin{equation}
  \label{eq:construction:qc1}
  \bigsqcup_i \vmark_i(\Gamma(\openset_i,\dtotal_i\restriction_{\openset_i})) = \bigsqcup_i \Gamma(\opensetg_i, \gtotal\restriction_{\opensetg_i})
\end{equation}
A property of hom-sets is that $Hom(W_i,H) + Hom(W_j,H) = Hom(W_i+W_j,H)$, which means that the union of hom-sets with the same target is equal to the hom-set of the union of sources to the target; therefore
\begin{equation}
  \label{eq:construction:qc2}
  \bigsqcup_i\Gamma(\opensetg_i, \gtotal\restriction_{\opensetg_i}) = \Gamma(\mathop{\sqcup}_{i}\opensetg_i, \gtotal\restriction_{{\mathop{\sqcup}_i}\opensetg_i})
\end{equation}
the union of sets of functions that generate parts of an image is equal to a set of functions that can generate the whole image. This implies that we can define a $\vmarkc$ that generates the set of sections over the whole image 
\begin{equation}
  \label{eq:construction:qc3}
\Gamma(\mathop{\sqcup}_i\opensetg_i, \gtotal\restriction_{\mathop{\sqcup}_{i}\opensetg_i}) \implies \vmark(\mathop{\sqcup}_{i}\Gamma(\openset_i,\vtotal_i\restriction_{\openset_i}) 
\end{equation}
which means that, following from \autoref{eq:constrution:qc1} and \autoref{eq:construction:qc3},
\begin{equation}
  \label{eq:construction:qc4}
  \vmarkc(\mathop{\sqcup}_{i}\cgamma{\opensetc_i}{\vtotalc_i\restriction_{\opensetc_i}}) =   
  \bigsqcup_i \vmarkc_i(\cgamma{\opensetc_i}{\vtotalc_i\restriction_{\opensetc_i}})
\end{equation}
we can construct a $\vmarkc = \sqcup_i\vmarkc_i$.v This allows us to .

\begin{figure}
  \label{fig:construction:combined_q}
  \includegraphics[width=1\colunwidth]{qsketchh.png}
  \caption{}
\end{figure}

As illustrated in \autoref{fig:construction:combined_q}, this composition rule expresses the construction of a multipart circle-square graphic out of circles and squares produced by different $\vmarkc$. \note{rewrite:Also figures are the unions of their parts}.

\subsubsection{Validating \vmarkc's}

\begin{tikzcd}[column sep=.5em, row sep=1em]
  \cgamma{\opensetc}{(\vtotalc^{a}\times \vtotalc^{b})\restriction_{\opensetc}} 
    \arrow[rr, "\vmarkc_{ab}", color=artist] 
    \arrow[dd, "\pi_a"', color=total]                &  & \imartistsub{ab}{\opensetgc}{\gtotalc\restriction_{\opensetgc}} \arrow[rd, "\extractmc_{ab}",color=monoid]   &                                                                                                   \\
                                                                                                                               &  &                                                                                                            & {{\textcolor{set}{Hom}(\opensetc, \measurec^{ab})}} \arrow[ld, "\measurec\restriction_{a}", color=set]  \\
  \cgamma{\opensetc}{\vtotalc^{a}\restriction_{\opensetc}} \arrow[rr, "\simeq", dotted]                                        &  & {{\textcolor{set}{Hom}(\opensetc, \measurec^{a})}}                                                         &                                                                                                   \\
                                                                                                                               &  &                                                                                                            & {{\textcolor{set}{Hom}(\opensetc, \measurec^{ac})}} \arrow[lu, "\measurec\restriction_{a}"', color=set] \\
  \cgamma{\opensetc}{(\vtotalc^{a}\times \vtotalc^{c})\restriction_{\opensetc}} \arrow[rr, "\vmarkc_{ac}", color=artist] \arrow[uu, "\pi_a", color=total] &  & \imartistsub{ac}{\opensetgc}{\gtotalc\restriction_{\opensetgc}} \arrow[ru, "\extractmc_{ac}"', color=monoid] &                                                                                                  
  \end{tikzcd}
\note{when $Q_{ab} = Q_{bc}$, this says only things that change are the parameter controlled pieces}

\subsection{Implementation Options: $\vartistc=\vmarkc\circ\vchannelc$}
As mentioned in \autoref{sec:atct:sheaves}, sheaves equipped with transport functors have isomorphic maps between the sheaves. This property allows us to specify the transformation from data to graphic space in data or graphic space or a mix of both such that the following diagram commutes:

\begin{tikzcd}[row sep=2.5em, column sep=1.5em]
  \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} 
  \arrow[rr, "\vchannelc", color=artist] 
  \arrow[rrrr, "\vartistc^{\dbasec}", bend left, color=artist] 
  \arrow[dd, "\vindexpullc"', color=functor] 
  \arrow[rrrrdd, "\vartistc", color=artist, pos=.2] &  & 
  \cgamma{\opensetc}{\vtotalc\restriction_{\opensetc}} 
  \arrow[rrdd, "\vmarkc", color=artist] 
  \arrow[rr, "\vmarkc^{\dbasec}", color=artist] 
  \arrow[dd, "\vindexpullc", color=functor, pos=.2] &  & \imartist{\opensetc}{\vindexpushc\gtotalc\restriction_{\opensetc}}  \\
   & & & & \\
  \cgamma{\opensetgc}{\vindexpullc\dtotalc\restriction_{\opensetgc}} \arrow[rr, "\vchannelc", color=artist] 
  \arrow[rrrr, "\vartistc^{\gbasec}", bend right, color=artist] & & 
  \cgamma{\opensetgc}{\vindexpullc\vtotalc\restriction_{\opensetgc}} \arrow[rr, "\vmarkc^{\gbasec}", color=artist] &  & 
  \imartist{\opensetgc}{\gtotalc\restriction_{\opensetgc}} \arrow[uu, "\vindexpushc"', color=functor]
\end{tikzcd}
